---
title: "HW 6"
author: "Nhu Nguyen"
date: "2023-12-06"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(dplyr)
library(knitr)

set.seed(1)
```

# Problem 1

# Problem 2

importing data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

creating 5000 bootstrap sample
```{r}
bootstrap_df = weather_df |> 
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df)),
    results = map(models, broom::tidy),
    rsq = map(models, broom::glance)) |> 
  select(results, .id, rsq) |> 
  unnest(results) |> 
  filter(term %in% c("tmin", "prcp")) |> 
  group_by(.id) |> 
  mutate(beta1xbeta2 = prod(estimate),
         log_beta_product = log(beta1xbeta2)) |> 
  select(log_beta_product, rsq) |> 
  unnest(rsq) |> 
  janitor::clean_names() |> 
  select(log_beta_product, id, r_squared) |> 
  unique()
```

### plotting distribution of estimates
log of beta product
```{r}
bootstrap_df |> 
  ggplot(aes(x = log_beta_product)) + geom_density()
```
This figure displays the distribution of the estimates of the log of the product of betas 1 and 2, which is left skewed and unimodal with a peak at around -5.75.


r-squared
```{r}
bootstrap_df |> 
  ggplot(aes(x = r_squared)) + geom_density()
```
This figure displays the distribution of the estimates of r-squared values, which is slightly left skewed (although almost normal) and unimodal with a peak at around 0.916.


95% CI
```{r}
bootstrap_conf = bootstrap_df |> 
  unique() |>
  ungroup() |> 
  select(-id) |> 
  summarize(beta_mean = mean(log_beta_product, na.rm = TRUE),
            beta_low = quantile(log_beta_product, 0.025, na.rm = TRUE),
            beta_high = quantile(log_beta_product, 0.975, na.rm = TRUE),
            rs_mean = mean(r_squared),
            rs_low = quantile(r_squared, 0.025),
            rs_high = quantile(r_squared, 0.975))

bootstrap_conf |> knitr::kable()
```
The 95% confidence interval for the log of the beta product is (`r bootstrap_conf$beta_low`, `r bootstrap_conf$beta_high`).

The 95% confidence interval for r-squared is (`r bootstrap_conf$rs_low`, `r bootstrap_conf$rs_high`).
