---
title: "HW 6"
author: "Nhu Nguyen"
date: "2023-12-06"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(dplyr)
library(knitr)

set.seed(1)
```

# problem 1

# problem 2

importing data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

creating 5000 bootstrap sample
```{r}
bootstrap_df = weather_df |> 
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df)),
    results = map(models, broom::tidy),
    rsq = map(models, broom::glance)) |> 
  select(results, .id, rsq) |> 
  unnest(results) |> 
  filter(term %in% c("tmin", "prcp")) |> 
  group_by(.id) |> 
  mutate(beta1xbeta2 = prod(estimate),
         log_beta_product = log(beta1xbeta2)) |> 
  select(log_beta_product, rsq) |> 
  unnest(rsq) |> 
  janitor::clean_names() |> 
  select(log_beta_product, id, r_squared) |> 
  unique()
```

### plotting distribution of estimates
log of beta product
```{r}
bootstrap_df |> 
  ggplot(aes(x = log_beta_product)) + geom_density()
```
This figure displays the distribution of the estimates of the log of the product of betas 1 and 2, which is left skewed and unimodal with a peak at around -5.75.


r-squared
```{r}
bootstrap_df |> 
  ggplot(aes(x = r_squared)) + geom_density()
```
This figure displays the distribution of the estimates of r-squared values, which is slightly left skewed (although almost normal) and unimodal with a peak at around 0.916.


95% CI
```{r}
bootstrap_conf = bootstrap_df |> 
  unique() |>
  ungroup() |> 
  select(-id) |> 
  summarize(beta_mean = mean(log_beta_product, na.rm = TRUE),
            beta_low = quantile(log_beta_product, 0.025, na.rm = TRUE),
            beta_high = quantile(log_beta_product, 0.975, na.rm = TRUE),
            rs_mean = mean(r_squared),
            rs_low = quantile(r_squared, 0.025),
            rs_high = quantile(r_squared, 0.975))

bootstrap_conf |> knitr::kable()
```
The 95% confidence interval for the log of the beta product is (`r bootstrap_conf$beta_low`, `r bootstrap_conf$beta_high`).

The 95% confidence interval for r-squared is (`r bootstrap_conf$rs_low`, `r bootstrap_conf$rs_high`).

# problem 3 

importing & cleaning dataset 
```{r}
bw_df = read.csv("birthweight.csv")

bw_df = bw_df |> 
  janitor::clean_names() |> 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)) |> 
  drop_na()
```

proposed regression model
```{r}
fit = lm(bwt ~ gaweeks + smoken + delwt + wtgain, data = bw_df)

fit |>
  broom::tidy() |>
  select(term, estimate, p.value) |>
  knitr::kable(digits=3)

summary(fit)
```

the proposed regression model is based on biological factors that have been proven to have an effect on the baby's weight, including `gaweeks`, gestational age in weeks, `smoken`, average number of cigarettes smoked per day during pregnancy, `delwt`, mother's weight at delivery in pounds, and `wtgain`, mother's weight gain during pregnancy in pounds. as the p0values for the predictors are all less than 0.01, the hypothesized predictors do not need to be removed from the model.

plotting residuals against fitted values
```{r}
bw_df |> 
  modelr::add_residuals(fit) |> 
  modelr::add_predictions(fit) |> 
  ggplot(aes(x = resid, y = pred)) +
  geom_point(alpha = 0.5)
```
the residual plot displays the majority of residual values being clustered around 0, with the avg. predicted birth weight hovering around 3250 grams


comparing model to two others 
```{r}
cv_df =
  crossv_mc(bw_df, 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```


```{r}
cv_df = cv_df |> 
  mutate(
    model_prop = map(train, \(df) lm(bwt ~ gaweeks + smoken + delwt + wtgain, data = df)),
    model_1 = map(train, \(df) lm(bwt ~ blength + gaweeks, data = df)),
    model_2 = map(train, \(df) lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = df))) |> 
  mutate(
    rmse_prop = map2_dbl(model_prop, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_1 = map2_dbl(model_1, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_2 = map2_dbl(model_2, test, \(mod, df) rmse(model = mod, data = df)))

cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

the plot shows the RMSE value distribution for the three different models. model 2 (comparison model for interaction terms) has the lowest RMSE values, indicating it has a better predictive performance than the proposed model and the model with only the main effects. the best fit is the model with the three-way interaction. 

